What's in a Name? \\ Linear Temporal Logic \\ Literally Represents Time Lines

### 2023-08-28 paper/main.tex
edits through end of sectin 3

        \caption{Example of one possible timeline for the specification ``$p$ oscillates every time step''}

@@

        \caption{Example of a timeline for the specification ``$a$ is eventually true''}

@@

\begin{algorithm}[h!]
    \caption{reduce\_nfa}
    \begin{algorithmic}
        \Require ($G, v$), an NFA with state $v$ that is not initial or final
        \Ensure Deletes state $v$ from $G$ while ensuring the same language is recognized
        \For{ every $u\xrightarrow{r_\mathrm{in}} v, v \xrightarrow{r_\mathrm{out}} w$ }
            \If {$v$ has a self-edge  $v\xrightarrow{r_\mathrm{loop}}v$}
                \State replace edges $u\xrightarrow{r_\mathrm{in}} v, v \xrightarrow{r_\mathrm{out}} w$ with $u \xrightarrow{r_\mathrm{in} r_\mathrm{loop}* r_\mathrm{out}} w$
            \Else
                \State replace edges $u\xrightarrow{r_\mathrm{in}} v, v \xrightarrow{r_\mathrm{out}} w$ with $u \xrightarrow{r_\mathrm{in}  r_\mathrm{out}} w$
            \EndIf
        \EndFor
	\State delete node $v$ from $G$
        %\State \Return the reduced graph $G$
    \end{algorithmic}
\end{algorithm}

\begin{algorithm}[h!]
    \caption{nfa2regex}
    \begin{algorithmic}
        \Require ($G, s, f$), an NFA with initial state $s$ and final state $f$
        \Ensure The regular expression corresponding to all paths from $s$ to $f$
        % WHile there exists any edge except r_sf
        \While{ there exists an interior vertex $v$ }
            \State reduce\_nfa($G, v$)
            \State combine multi-edges, i.e., $r1 : u \to w, r2 : u \to w$  to $r1 | r2 : u \to w$
        \EndWhile
        \State \Return $(r_\mathrm{ss}| r_\mathrm{sf} r_\mathrm{ff}^* r_\mathrm{fs})^* r_\mathrm{sf} r_\mathrm{ff}$
        % if called by first visit, this is r_\mathrm{ss}* r_\mathrm{sf}
        % if called by ba2wregex, s=f, this is r_\mathrm{ff}
        % consider modularizing fns differently
        % \State \Return regexp labelling the edge $s\to f$
    \end{algorithmic}
\end{algorithm}

\begin{algorithm}[h!]
    \caption{nfa2regex\_firstvisit}
    \begin{algorithmic}
        \Require ($G, s, f$), an NFA with initial state $s$ and final state $f$
        \Ensure The regular expression of all paths from $s$ reaching $f$ for the first time
        \State delete all out edges from $f$ in $G$
        \State \Return nfa2regex($G, s, f$)
    \end{algorithmic}
\end{algorithm}

@@

The $\omega$-regular expression generated in \cref{aut2regex} may not be the ``simplest'' for the purpose of visualizing the timeline. We have observed multiple patterns in the resulting $\omega$-regular expression that could be simplified. For example, an $\omega$-regular expression in the form of $r^*r^{\omega}$ represents the same timeline as $r^{\omega}$, but the latter is more intuitive and concise. For this purpose, we devised some simplification rules in our tool, based on our observation of common patterns in the generated $\omega$-regular expression.

There is no agreed upon canonical form for regular expression, hence we do not hope to find the simplest regular expression for visualization. Regular expression simplification comes down to regular expression equivalence checking, which is computationally hard~\cite{MNS04}. For purpose of simplification, one could perform a search over equivalent regular expressions and decide which one is simpler to use. However, this strategy is expensive in terms of the running time, and for the purpose of visualization, we did not use this strategy in our tool. We consider this approach as future work.

@@

\paragraph*{Result of simplification}
These simplification rules lead to more intuitive representation of timelines. Here we demonstrate their effects using an example.

@@

    Using our algorithm, the \ltl\ formula $\varphi = \always (a \limplies \eventually (\neg a))$ generates the un-simplified $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))((\lnot a) | (aa^*(\lnot a)))^{\omega}$, and the simplified version $((\lnot a) | (aa^*(\lnot a)))^{\omega}$, which correspond to the two timelines in \cref{fig:unsimplified} and \cref{fig:simplified}.

@@

        $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))((\lnot a) | (aa^*(\lnot a)))^{\omega}$}

@@

        \caption{Timeline visualization for simplified $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))^{\omega}$}

@@

\begin{remark}
    Both simplified and un-simplified $\omega$-regular expressions would generate correct timeline representations. Correct as they faithfully represent the set of satisfying traces of the original \ltl\ formula $\varphi$. Nonetheless, we, as human users, oftentimes find the simplified version more intuitive to reason about.
\end{remark}

\subsection{$\omega$-regex to timeline} \label{regex2timeline}
Our tool uses Graphviz~\cite{Ellson2001GraphvizO} to achieve the timeline visualization step. By construction of our algorithm, every $\omega$-regular expression is in the form of
\[
    A_1A_2^{\omega} + A_3A_4^{\omega} + \cdots + A_{2n-1}A_{2n}^{\omega}
\]
where $A_i$ are regular expressions, $A_{2i-1}$ could be $\epsilon$, and $\epsilon \not\in \L(A_{2i})$. At a high level, for each of regular expression $A_i$, we visualize it as a set of accepted input. We view each union operator as parallel timelines, and each $A_{2i-1}$ is concatenated with $A_{2i}$ repeated infinitely many times, as represented in the grey box. \cref{fig:timeline} presents a generic timeline resulting from this form of construction.
\begin{figure}[h!]
    \centering
    \begin{tikzpicture}
    \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a1) {$A_1$};
    \node[shape=rectangle, fill=gray!30!white, style={minimum width=1.8cm, minimum height=1.3cm}] (a2g) [right= 0.85cm of a1] {};
    \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a2) [right= 1cm of a1] {$A_2$};
    \node[draw, thick, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a3) [below= 0.4cm of a1] {$A_3$};
    \node[shape=rectangle, fill=gray!30!white, style={minimum width=1.8cm, minimum height=1.3cm}] (a4g) [right= 0.85cm of a3] {};
    \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a4) [right= 1cm of a3] {$A_4$};
    \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a5) [below= 0.4cm of a3] {...};
    \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a7) [below= 0.4cm of a5] {\!\!\!$A_{2n-1}$\!\!\!};
    \node[shape=rectangle, fill=gray!30!white, style={minimum width=1.8cm, minimum height=1.3cm}] (a8g) [right= 0.85cm of a7] {};
    \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a8) [right= 1cm of a7] {\!\!\!$A_{2n}$\!\!\!};
    \node (m) at ($(a1)!0.5!(a7)$) {};
    \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (s) [left= 1.5cm of m] {\!\!\!\!start\!\!\!\!};
    \draw[thick] (s) edge[-latex] (a1) (s) edge[-latex] (a3) (s) edge[-latex] (a5) (s) edge[-latex] (a7);
    \draw[thick] (a1) edge[-latex] (a2) (a3) edge[-latex] (a4) (a7) edge[-latex] (a8);
    \end{tikzpicture}
%    \includegraphics[scale=0.5]{img/timeline.png}
    \caption{Generic timeline construction from $A_1A_2^{\omega} + A_3A_4^{\omega} + \cdots + A_{2n-1}A_{2n}^{\omega}$}
    \label{fig:timeline}
\end{figure}

@@

We prove the correctness of our translation pipeline. The correctness of the translation from LTL formulas to \Buchi automata is provided by SPOT~\cite{Dur22}. Below, we prove the correctness of (i) the translation from \Buchi automata to $\omega$-regular expressions, (ii) the ($\omega$-)regular expression rewrite rules we apply, and lastly, we outline the correctness of our timeline visualizations.
\subsection{Correctness of Regex Translation}
\begin{lemma}
    % reduce_nfa does its input to output behaviour
    For any NFA $G$ and any state $v$ in $G$ that is neither a start state or a final state, \textbf{reduce\_nfa}$(G, v)$ preserves the regular language accepted by $G$
\end{lemma}
\begin{proof}
    Let $G'$ be the graph of $G$ post reduction by the application of \textbf{reduce\_nfa}$(G, v)$. We show that the trace of every path accepted by $G$ is also accepted by $G'$. Suppose a path accepted by $G$ does not pass through $v$, clearly this is true. Else, suppose it passes through $v$, since $v$ is an interior node, $v$ cannot be the first or last in the path. Thus, for every pass through $v$, let $u\neq v$ be the last node passed before entering $v$, and likewise $w$ be the first node after exiting $v$. We show that the regular language of sub-traces from $u$ to $w$ in $G$ (shown in \cref{fig:uvw-dfa}) is identical to that in $G'$.
    \begin{figure}[h!]
        \centering
        \begin{tikzpicture}
	\node[draw, thick, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (u) {$u$};
	\node[draw, thick, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (v) [right=of u] {$v$};
	\node[draw, thick, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (w) [right=of v] {$w$};
	\draw[thick] (u) edge["$r_{uv}$",-latex] (v) (v) edge["$r_{vv}$",-latex,loop above] (v) (v) edge["$r_{vw}$",-latex] (w);
        \end{tikzpicture}
 %       \includegraphics[scale=0.75]{img/uvw_dfa.pdf}
        \caption{A path from $u$ to $w$ in $G$}
        \label{fig:uvw-dfa}
    \end{figure}
    Suppose there is no loop at $v$, the path from $u$ to $w$ must simply be $u\xrightarrow{r_{uv}}v\xrightarrow{r_{vw}}w$, with the trace $r=r_{uv}r_{vw}$. If there is a loop edge $r_{vv}$, this edge can be traveled any number of times before exiting $v$, thus the regular expression is $r=r_{uv}r_{vv}^*r_{vw}$. This edge $u\xrightarrow{r}w$ is added in $G'$. Thus, for every path accepted by $G$, for every subpath entering and exiting $v$ from some $u$ to $w$, there exists a corresponding subpath from $u$ to $w$ in $G'$, and thus a corresponding path accepted by $G'$.
\end{proof}

@@

     %   \includegraphics[scale=0.3]{examples/ex14/ex14.png}
        \caption{Timeline for $\always (a \land b \limplies \nextt (\neg b))$}
        \label{fig:ex14}
    \end{figure*}
\end{example}

@@

   %     \includegraphics[scale=0.3]{examples/ex13/ex13.png}
        \caption{Timeline for $p_2 \land (\eventually \always p_0 \stronguntil \nextt(\always p_1 \land (((p_0 \limplies p_2) \land (p_2 \limplies p_0)) \stronguntil \eventually p_0)))$}
        \label{fig:ex13}
    \end{figure*}
\end{example}
\begin{remark}
    These two examples show that our tool can generate reasonably clear diagrams for both real-world formula and randomly generated formula.
\end{remark}

@@

  \caption{Timeline for $\always ((p \land \nextt (\lnot p)) \lor ((\lnot p) \land \nextt p))$}

@@

  \caption{Timeline for $\always ((p \land \nextt (\lnot p)) \land ((\lnot p) \land \nextt p))$ (a single ``start'' means every time step is $\bot$)}

@@

\begin{figure}[h!]
    \centering
    \subfloat{{\includegraphics[width=0.49\textwidth]{img/tllens-graph.png} }}%
    \quad % [\centering label 1]
    \subfloat{{\includegraphics[width=0.49\textwidth]{img/star-height-graph.png}}}
    \caption{Visualization complexity metrics for formulas collected from Acacia~\cite{RV10} and NASA's  AAC~\cite{GCMTR16}}
    \label{fig:real-world}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.49\textwidth]{img/binary.png}
    \caption{Scalability measured with binary counter examples from Rozier and Vardi~\cite{RV10}}
    \label{fig:scalability}
\end{figure}

>>>>

        \caption{Example of one possible timeline for the specification ``$p$ oscillates every time step.''}

@@

        \caption{Example of a timeline for the specification ``$a$ is eventually true.''}

@@

\begin{algorithm}[h!]
    \caption{reduce\_nfa}
    \begin{algorithmic}
        \Require ($G, v$): NFA $G$ with state $v$ that is not initial or final
        \Ensure Deletes state $v$ from $G$ while ensuring $\L(G)$ remains unchanged
        \For{ every $u\xrightarrow{r_\mathrm{in}} v, v \xrightarrow{r_\mathrm{out}} w$ }
            \If {$v$ has a self-edge  $v\xrightarrow{r_\mathrm{loop}}v$}
                \State replace edges $u\xrightarrow{r_\mathrm{in}} v, v \xrightarrow{r_\mathrm{out}} w$ with $u \xrightarrow{r_\mathrm{in} r_\mathrm{loop}* r_\mathrm{out}} w$
            \Else
                \State replace edges $u\xrightarrow{r_\mathrm{in}} v, v \xrightarrow{r_\mathrm{out}} w$ with $u \xrightarrow{r_\mathrm{in}  r_\mathrm{out}} w$
            \EndIf
        \EndFor
	\State delete node $v$ from $G$
        %\State \Return the reduced graph $G$
    \end{algorithmic}
\end{algorithm}

\begin{algorithm}[h!]
    \caption{nfa2regex}
    \begin{algorithmic}
        \Require ($G, s, f$): NFA $G$ with initial state $s$ and final state $f$
        \Ensure The regular expression corresponding to all paths from $s$ to $f$
        % WHile there exists any edge except r_sf
        \While{ there exists an interior vertex $v$ }
            \State reduce\_nfa($G, v$)
            \State combine multi-edges, i.e., convert $r1 : u \to w, r2 : u \to w$  to $r1 | r2 : u \to w$
        \EndWhile
        \State \Return $(r_\mathrm{ss}| r_\mathrm{sf} r_\mathrm{ff}^* r_\mathrm{fs})^* r_\mathrm{sf} r_\mathrm{ff}$
        % if called by first visit, this is r_\mathrm{ss}* r_\mathrm{sf}
        % if called by ba2wregex, s=f, this is r_\mathrm{ff}
        % consider modularizing fns differently
        % \State \Return regexp labelling the edge $s\to f$
    \end{algorithmic}
\end{algorithm}

\begin{algorithm}[h!]
    \caption{nfa2regex\_firstvisit}
    \begin{algorithmic}
        \Require ($G, s, f$):  NFA $G$ with initial state $s$ and final state $f$
        \Ensure The regular expression of all paths from $s$ reaching $f$ for the first time
        \State delete all out edges from $f$ in $G$
        \State \Return nfa2regex($G, s, f$)
    \end{algorithmic}
\end{algorithm}

@@

The $\omega$-regular expression generated in \cref{aut2regex} may not be the ``simplest'' for the purpose of visualizing the timeline. We have observed multiple patterns in the resulting $\omega$-regular expression that could be simplified. For example, an $\omega$-regular expression of the form of $r^*r^{\omega}$ represents the same timeline as $r^{\omega}$, but the latter is more intuitive and concise. For this purpose, we devised some simplification rules in our tool, based on our observation of common patterns in the generated $\omega$-regular expressions.

There is no agreed-upon canonical form for regular expressions representing \ltl\ formulas, hence we do not hope to find the shortest possible regular expression for visualization. Regular expression simplification comes down to regular expression equivalence checking, which is computationally hard~\cite{MNS04}. For purpose of simplification, one could perform a search over equivalent regular expressions and decide which one is simpler to use. However, this strategy is expensive in terms of the running time, and for the purpose of visualization, we did not use this strategy in our tool. We consider simplification for the purpose of finding the most intuitive regular expression for a given \ltl\ formula to be an interesting direction for future work.

@@

\paragraph*{Result of simplification}
These simplification rules lead to more intuitive representations of timelines. Here we demonstrate their effects using an example.

@@

    Using our algorithm, the \ltl\ formula $\varphi = \always (a \limplies \eventually (\neg a))$ generates the un-simplified $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))((\lnot a) | (aa^*(\lnot a)))^{\omega}$, and the simplified version $((\lnot a) | (aa^*(\lnot a)))^{\omega}$, which correspond to the two timelines in \cref{fig:unsimplified} and \cref{fig:simplified}, respectively.

@@

        $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))((\lnot a) | (aa^*(\lnot a)))^{\omega}$.}

@@

        \caption{Timeline visualization for simplified $\omega$-regular expression $((\lnot a) | (aa^*(\lnot a)))^{\omega}$.}

@@

\begin{remark}
    Both simplified and un-simplified $\omega$-regular expressions could generate correct timeline representations that faithfully represent the set of satisfying traces of the original \ltl\ formula $\varphi$. Nonetheless, we, as human users, oftentimes find the simplified version more intuitive to reason about.
\end{remark}

\subsection{$\omega$-regex to timeline} \label{regex2timeline}
Our tool uses Graphviz~\cite{Ellson2001GraphvizO} to achieve the timeline visualization step. By construction of our algorithm, every $\omega$-regular expression is in the form of
\[
    A_1A_2^{\omega} + A_3A_4^{\omega} + \cdots + A_{2n-1}A_{2n}^{\omega}
\]
where $A_i$ are regular expressions, $A_{2i-1}$ could be $\epsilon$, and $\epsilon \not\in \L(A_{2i})$. At a high level, we visualize each regular expression $A_i$ as a set of accepted inputs. We view each union operator as a set of parallel timelines. We denote that each $A_{2i-1}$ gets concatenated with $A_{2i}$, which then repeats infinitely many times by surrounding these repeating final nodes with grey boxes. \cref{fig:timeline} presents a generic timeline resulting from this construction pattern.
\begin{figure}[h!]
    \centering
    \begin{tikzpicture}
    \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a1) {$A_1$};
    \node[shape=rectangle, fill=gray!30!white, style={minimum width=1.8cm, minimum height=1.3cm}] (a2g) [right= 0.85cm of a1] {};
    \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a2) [right= 1cm of a1] {$A_2$};
    \node[draw, thick, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a3) [below= 0.4cm of a1] {$A_3$};
    \node[shape=rectangle, fill=gray!30!white, style={minimum width=1.8cm, minimum height=1.3cm}] (a4g) [right= 0.85cm of a3] {};
    \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a4) [right= 1cm of a3] {$A_4$};
    \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a5) [below= 0.4cm of a3] {...};
    \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a7) [below= 0.4cm of a5] {\!\!\!$A_{2n-1}$\!\!\!};
    \node[shape=rectangle, fill=gray!30!white, style={minimum width=1.8cm, minimum height=1.3cm}] (a8g) [right= 0.85cm of a7] {};
    \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a8) [right= 1cm of a7] {\!\!\!$A_{2n}$\!\!\!};
    \node (m) at ($(a1)!0.5!(a7)$) {};
    \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (s) [left= 1.5cm of m] {\!\!\!\!start\!\!\!\!};
    \draw[thick] (s) edge[-latex] (a1) (s) edge[-latex] (a3) (s) edge[-latex] (a5) (s) edge[-latex] (a7);
    \draw[thick] (a1) edge[-latex] (a2) (a3) edge[-latex] (a4) (a7) edge[-latex] (a8);
    \end{tikzpicture}
%    \includegraphics[scale=0.5]{img/timeline.png}
    \caption{Generic timeline construction created from $A_1A_2^{\omega} + A_3A_4^{\omega} + \cdots + A_{2n-1}A_{2n}^{\omega}$.}
    \label{fig:timeline}
\end{figure}

@@

We prove the correctness of our translation pipeline. The correctness of the translation from LTL formulas to \Buchi automata is provided by SPOT~\cite{Dur22}. Below, we prove the correctness of (i) the translation from \Buchi automata to $\omega$-regular expressions, (ii) the ($\omega$-)regular expression rewrite rules we apply, and lastly, we outline the correctness of our timeline visualizations.
\subsection{Correctness of Regex Translation}
\begin{lemma}
    % reduce_nfa does its input to output behaviour
    For any NFA $G$ and any state $v$ in $G$ that is neither a start state or a final state, \textbf{reduce\_nfa}$(G, v)$ preserves the regular language accepted by $G$
\end{lemma}
\begin{proof}
    Let $G'$ be the graph of $G$ post reduction by the application of \textbf{reduce\_nfa}$(G, v)$. We show that the trace of every path accepted by $G$ is also accepted by $G'$. Suppose a path accepted by $G$ does not pass through $v$, clearly this is true. Else, suppose it passes through $v$, since $v$ is an interior node, $v$ cannot be the first or last in the path. Thus, for every pass through $v$, let $u\neq v$ be the last node passed before entering $v$, and likewise $w$ be the first node after exiting $v$. We show that the regular language of sub-traces from $u$ to $w$ in $G$ (shown in \cref{fig:uvw-dfa}) is identical to that in $G'$.
    \begin{figure}[h!]
        \centering
        \begin{tikzpicture}
	\node[draw, thick, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (u) {$u$};
	\node[draw, thick, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (v) [right=of u] {$v$};
	\node[draw, thick, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (w) [right=of v] {$w$};
	\draw[thick] (u) edge["$r_{uv}$",-latex] (v) (v) edge["$r_{vv}$",-latex,loop above] (v) (v) edge["$r_{vw}$",-latex] (w);
        \end{tikzpicture}
 %       \includegraphics[scale=0.75]{img/uvw_dfa.pdf}
        \caption{A path from $u$ to $w$ in $G$.}
        \label{fig:uvw-dfa}
    \end{figure}
    Suppose there is no loop at $v$, the path from $u$ to $w$ must simply be $u\xrightarrow{r_{uv}}v\xrightarrow{r_{vw}}w$, with the trace $r=r_{uv}r_{vw}$. If there is a loop edge $r_{vv}$, this edge can be traveled any number of times before exiting $v$, thus the regular expression is $r=r_{uv}r_{vv}^*r_{vw}$. This edge $u\xrightarrow{r}w$ is added in $G'$. Thus, for every path accepted by $G$, for every subpath entering and exiting $v$ from some $u$ to $w$, there exists a corresponding subpath from $u$ to $w$ in $G'$, and thus a corresponding path accepted by $G'$.
\end{proof}

@@

     %   \includegraphics[scale=0.3]{examples/ex14/ex14.png}
        \caption{Timeline for $\always (a \land b \limplies \nextt (\neg b))$.}
        \label{fig:ex14}
    \end{figure*}
\end{example}

@@

   %     \includegraphics[scale=0.3]{examples/ex13/ex13.png}
        \caption{Timeline for $p_2 \land (\eventually \always p_0 \stronguntil \nextt(\always p_1 \land (((p_0 \limplies p_2) \land (p_2 \limplies p_0)) \stronguntil \eventually p_0)))$.}
        \label{fig:ex13}
    \end{figure*}
\end{example}
\begin{remark}
    These two examples show that our tool can generate reasonably clear diagrams for both real-world formula and randomly generated formula.
\end{remark}

@@

  \caption{Timeline for $\always ((p \land \nextt (\lnot p)) \lor ((\lnot p) \land \nextt p))$.}

@@

  \caption{Timeline for $\always ((p \land \nextt (\lnot p)) \land ((\lnot p) \land \nextt p))$ (a single ``start'' means every time step is $\bot$).}

@@

\begin{figure}[h!]
    \centering
    \subfloat{{\includegraphics[width=0.49\textwidth]{img/tllens-graph.png} }}%
    \quad % [\centering label 1]
    \subfloat{{\includegraphics[width=0.49\textwidth]{img/star-height-graph.png}}}
    \caption{Visualization complexity metrics for formulas collected from Acacia~\cite{RV10} and NASA's  AAC~\cite{GCMTR16}.}
    \label{fig:real-world}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.49\textwidth]{img/binary.png}
    \caption{Scalability measured with binary counter examples from Rozier and Vardi~\cite{RV10}.}
    \label{fig:scalability}
\end{figure}
